---
title: "TERN"
author: "Pascal Bärschi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# `g_lineplot`

## read in data

```{r}
library(nestcolor)
library(tern)


adsl <- tern_ex_adsl
adlb <- tern_ex_adlb %>% dplyr::filter(ANL01FL == "Y", PARAMCD == "ALT", AVISIT != "SCREENING")
adlb$AVISIT <- droplevels(adlb$AVISIT)
adlb <- dplyr::mutate(adlb, AVISIT = forcats::fct_reorder(AVISIT, AVISITN, min))
```



## Mean with CI
```{r}
g_lineplot(adlb, adsl, subtitle = "Laboratory Test:")
```


## Mean with CI, no stratification

```{r}
g_lineplot(adlb, variables = control_lineplot_vars(strata = NA))
```



## Mean, upper whisker of CI, no strata counts N

```{r}
g_lineplot(
  adlb,
  whiskers = "mean_ci_upr",
  title = "Plot of Mean and Upper 95% Confidence Limit by Visit"
)
```



## Median with CI

```{r}
g_lineplot(
  adlb,
  adsl,
  mid = "median",
  interval = "median_ci",
  whiskers = c("median_ci_lwr", "median_ci_upr"),
  title = "Plot of Median and 95% Confidence Limits by Visit"
)
```


## Mean, +/- SD
```{r}
g_lineplot(adlb, adsl,
  interval = "mean_sdi",
  whiskers = c("mean_sdi_lwr", "mean_sdi_upr"),
  title = "Plot of Median +/- SD by Visit"
)
```



##  Mean with CI plot with stats table

```{r}
g_lineplot(adlb, adsl, table = c("n", "mean", "mean_ci"))
```



## Mean with CI, table and customized confidence level

```{r}
g_lineplot(
  adlb,
  adsl,
  table = c("n", "mean", "mean_ci"),
  control = control_analyze_vars(conf_level = 0.90),
  title = "Plot of Mean and 80% Confidence Limits by Visit"
)
```


## Mean with CI, table, filtered data

```{r}
adlb_f <- dplyr::filter(adlb, ARMCD != "ARM A" | AVISIT == "BASELINE")
g_lineplot(adlb_f, table = c("n", "mean"))
```
```{r}
#' create listing from a dataset
#' @param df dataset to be displayed
#' @param cols columns to be displayed
#' @param index_col columns to be treated as index (label rows)
#' @param formats format of each columns, if length is 1, this format applies to all
#' column. otherwise length should be the same as cols.
#' @param level integer indicating the depth. should not be touched by users.
as_listing <- function(df, cols = NULL, index_col = NULL, formats = NULL, level = 1L) {
  if (is.null(formats)) {
    formats <- rep(list(NULL), length(cols))
  }
  nc <- length(cols)
  if (nc == 0) {
    stop("listing should have non-empty `cols` argument")
  }
  if (length(index_col) == 0) {
    body <- lapply(seq_len(nrow(df)), function(i){
      r <- df[i, cols, drop = FALSE]
      cells <- Map(rcell, x = r, format = formats)
      return(rrowl("", cells))
    })
    body <- unlist(body, recursive = FALSE)
    header <- rrowl(NULL, var_label(df#, fill = TRUE
    )[cols])
    # why add this? I forgot. I remembered. to ensure that when there are multiple levels of columns,
    # the columns will not be reorderd; in addition, the manual columns will not be combined.
    #head <- lapply(seq_len(level), 
    #  function(l) {
    #    if (l == level) {
    #      rrowl(NULL, var_label(df, fill = TRUE)[cols])
    #    } else {
    #      rrowl(NULL, rep(c(' ', '  '), nc)[seq_len(nc)])
    #    }
    #  }
    #)
    #.lst <- lapply(head, function(x) unlist(row_values(x)))
    #fullcolinfo <- manual_cols(.lst = .lst)
    #fullbusiness <- names(collect_leaves(coltree(fullcolinfo)))
    #vals <- lapply(head, function(x) unlist(row_values(x)))
    #cspans <- lapply(head, rtables:::row_cspans)
    #repvals <- mapply(function(v, csp) rep(v, times = csp), v = vals, csp = cspans, SIMPLIFY = FALSE)
    #wanted <- rtables:::paste_em_n(repvals, length(repvals))
    #col_per_nc <- length(fullbusiness) / nc
    #fullbusiness_split <- split(fullbusiness, rep(seq_len(nc), rep(col_per_nc, nc)))
    #wantcols <- mapply(match, wanted, fullbusiness_split, USE.NAMES = FALSE) + seq(0, nc - 1) * col_per_nc 
    #header <- rtables:::subset_cols(fullcolinfo, wantcols)
    return(rtable(header = header, body))
  } else {
    findex <- index_col[1]
    dfs <- split(df, df[[findex]], drop = TRUE)
    dfs <- lapply(dfs, function(x){
      var_label(x) <- var_label(df)
      return(x)
    })
    tbls <- mapply(as_listing, df = dfs, MoreArgs = list(cols = cols, index_col = index_col[-1], formats = formats, level = level + 1L))
    colinfo <- tbls[[1]]@col_info
    tbl_with_label <- lapply(names(tbls), function(nm) {
      vtbl <- TableTree(
        cont = ElementaryTable(kids = list(), name = nm, cinfo = colinfo),
        labelrow = LabelRow(0L, nm, cinfo = colinfo),
        kids = tbls[nm],
        cinfo = colinfo
      )
    })
    
    ret <- TableTree(
      kids = tbl_with_label,
      cinfo = colinfo,
      cont = ElementaryTable(kids = list(), name = "", cinfo = colinfo)
    )
    #top_left_text <- var_label(df, fill = TRUE)[index_col]
    #top_left_indented <- sprintf("%s%s", stringr::str_dup("  ", seq_len(length(top_left_text)) - 1), top_left_text)
    #top_left(ret) <- top_left_indented
    return(ret)
  }
}
```

```{r}
as_listing(adsl, cols = "STUDYID")
```
#  `analyize_vars_as_cols`

## data preparation

```{r}
library(dplyr)
library(tern)

# Data preparation
adpp <- tern_ex_adpp %>% h_pkparam_sort()

lyt <- basic_table() %>%
  split_rows_by(var = "STRATA1", label_pos = "topleft") %>%
  split_rows_by(
    var = "SEX",
    label_pos = "topleft",
    child_label = "hidden"
  ) %>% # Removes duplicated labels
  analyze_vars_in_cols(vars = "AGE")
result <- build_table(lyt = lyt, df = adpp)
result
```

## By selecting just some statistics and ad-hoc labels
```{r}

lyt <- basic_table() %>%
  split_rows_by(var = "ARM", label_pos = "topleft") %>%
  split_rows_by(
    var = "SEX",
    label_pos = "topleft",
    child_labels = "hidden",
    split_fun = drop_split_levels
  ) %>%
  analyze_vars_in_cols(
    vars = "AGE",
    .stats = c("n", "cv", "geom_mean"),
    .labels = c(
      n = "aN",
      cv = "aCV",
      geom_mean = "aGeomMean"
    )
  )
result <- build_table(lyt = lyt, df = adpp)
result

```


## Changing row labels

```{r}
# Changing row labels
lyt <- basic_table() %>%
  analyze_vars_in_cols(
    vars = "AGE",
    row_labels = "some custom label"
  )
result <- build_table(lyt, df = adpp)
result
```


## Pharmacokinteric parameters

```{r}
# Pharmacokinetic parameters
lyt <- basic_table() %>%
  split_rows_by(
    var = "TLG_DISPLAY",
    split_label = "PK Parameter",
    label_pos = "topleft",
    child_label = "hidden"
  ) %>%
  analyze_vars_in_cols(
    vars = "AVAL"
  )
result <- build_table(lyt, df = adpp)
result
```


## Muliple calls (summarize labels and analyze underneath)

```{r}
# Multiple calls (summarize label and analyze underneath)
lyt <- basic_table() %>%
  split_rows_by(
    var = "TLG_DISPLAY",
    split_label = "PK Parameter",
    label_pos = "topleft"
  ) %>%
  analyze_vars_in_cols(
    vars = "AVAL",
    do_summarize_row_groups = TRUE # does a summarize level
  ) %>%
  split_rows_by("SEX",
    child_label = "hidden",
    label_pos = "topleft"
  ) %>%
  analyze_vars_in_cols(
    vars = "AVAL",
    split_col_vars = FALSE # avoids re-splitting the columns
  )
result <- build_table(lyt, df = adpp)
result
```



